

---
title: 'Visualization IsoQuant output'
output:
  html_document:
    theme: united
    df_print: kable
date: 'Compiled: `r format(Sys.Date(), "%B %d, %Y")`'
---

```{r}
library(reticulate)
library(glue)

conda_path <- "../miniconda3/envs/R_45_python310/" # Replace the path to your conda envirnment path
viewer_code_path <- "../IsoQuant_pipeline/utilities/adapter_isoquantviewer.R" # Replace the path to your location of the R code

use_condaenv(conda_path, required = TRUE) 
use_python(glue("{conda_path}/bin/python"), required = TRUE)
source(viewer_code_path) 
py_config() # for checking if the session is configured with the environment you specified
```


```{r}
output_directory <- "../prefix/results/isoquant_output/" # path to IsoQuantOutput directory
prefix <- "prefix" # Name of the project
reference_gtf <- '~/Documents/ref/geneannotations.gff3' # path to reference gene annotation 
viewer<-isoquantViewer(output_directory = output_directory,        
    prefix = prefix, 
    reference_gtf = reference_gtf,
    plot_output = '~/Desktop/'
      )

# * Plots are automatically saved in the folder "./plot_output" if plot_output is not defined
```

#### Visualizing read assignment and counts

Function: 

* plot_pie_assignment

  Plot pie chart of read assignment (.read_assignments.tsv.gz; stored as .reads_assignment) from IsoQuant. "feature_to_plot" are: "assignment_type", "gene_assignment", "Classification"


* plot_count_bar

  A bar plot of counts for either specified genes or isoforms. If providing gene_list, plots stacked barplot of isoforms per gene. If providing isoform_list, plots a barplot of specified isoforms.

  Can either be from the raw count or TPM matrix using "layer", and based on the transcript model or the reference annotation (use_transcript_model=True or False, default is False). Default is plotting all available samples, but can be limited to specific sample using "sample_id" = [sample1, sample2, and etc.]


```{r}
fname<-plot_count_bar(viewer,layer='count',
          isoform_list = list('ENST00000008440','transcript92.Y.nnic'),
          use_transcript_model=TRUE)
knitr::include_graphics(as.character(fname))

fname<-plot_pie_assignment(viewer,feature_to_plot = 'assignment_type')
knitr::include_graphics(as.character(fname))
```

#### Visualizing transcripts within a genomic region 

* plot_transcript_map

  Visualize transcript(s) for specified gene(s)/ensembl ID within the corresponding genomic region(s). Can be based on the transcript model or the reference genome. (Based on IsoQuant:plot_transcript_map) 

```{r}

fname<-plot_transcript_map(viewer,
                    gene_names=list("TSPAN6"),
                    use_transcript_model=TRUE)
knitr::include_graphics(as.character(fname))

```

* plot_genomic_region

  Visualize a genomic region defined by setting either:
  
    * region = 'X:100627109-100639991'
    * gene_name = 'TSPAN6'
    * or Ensembl_ID = 'ENSG00000000003'
  
  using pyGenomeTracks classes (https://pygenometracks.readthedocs.io/en/latest/).

  The default ordered tracks being plotted are ['ref','model','reads'],can be set using "plot_tracks".
    * 'ref': Reference GTF
    * 'model': IsoQuant transcript model GTF
    * 'reads': IsoQuant corrected alignment BED

  The default parameters for each track can be overwritten using tracks_params, by setting key-value pairs for any supported track property. (See the list of all available options at at https://pygenometracks.readthedocs.io/en/latest/content/all_tracks.html)



```{r,out.height="100%"}
fname<-plot_genomic_region(viewer,
                    gene_name = 'TSPAN6')
knitr::include_graphics(as.character(fname))

```
